Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: fig frames

In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
the {\sc Parspec} implementation of each theory and give credit to the papers
which calculated the QNMs.

@@

We now turn our attention to dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with (dashed line) and without (solid line) spin corrections to
dominant $l = m = 2$,~$n=0$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case.
%
We must remember that in the {\sc Parspec} formalism that the GR deviations
are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
We verified that these quantities do indeed peak at zero indicating consistency with GR.
%
We also see that in both cases, that the inclusion leading-order-in-spin
correction to the mode, displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

We also found for both GW events, that the
perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc Parspec}
formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
%
This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
and that is why we quoted only the $j=0$ bound above.

@@

\subsubsection{Effective-field-theory of general relativity}
\label{sec:results_efts}

>>>>

In Table~\ref{tab:ref_theories_qnms} we summarize the relevant parameters for
the {\sc ParSpec} implementation of each theory and give credit to the papers
which calculated the QNMs.

@@

We now turn our attention to dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with (dashed line) and without (solid line) spin corrections to
dominant $l = m = 2$,~$n=0$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case.
%
We must remember that in the {\sc ParSpec} formalism that the GR deviations
are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
We verified that these quantities do indeed peak at zero indicating consistency with GR.
%
We also see that in both cases, that the inclusion leading-order-in-spin
correction to the mode, displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

We also found for both GW events, that the
perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc ParSpec}
formalism is violated for the $\gamma_{\rm CS} \, \delta \tau^{(1)}$ coefficient.
%
This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
and that is why we quoted only the $j=0$ bound above.

@@

\subsubsection{cubic effective-field-theory of general relativity}
\label{sec:results_ceft}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/ceft_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm cEFT}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
in spin QNM correction.
%
\hs{TODO}
}
\label{fig:cEFT_exec_sum}
\end{figure}

\subsubsection{quartic effective-field-theory of general relativity}
\label{sec:results_qeft}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
%
In all panels, we use solid and dashed lines to correspond to the inclusion or not of the linear
in spin QNM correction.
%
\hs{TODO}
}
\label{fig:qEFT_exec_sum}
\end{figure}
